---
title: "Análise João Gabriel"
author: "João Gabriel Quaresma; Luis Anunciacao, PhD"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    theme: paper
    toc: yes
    toc_float:
      collapsed: no
      smooth_scroll: no
editor_options: 
  chunk_output_type: inline
---
## Packages

```{r}
pacman::p_load(tidyverse, janitor, stringr, psych, corrr, ggcorrplot, gmodels, arsenal,rsvd, lavaan,semPlot, dplyr, nnet)
```

## Get data

This code downloads all data from previous publication.

```{r}
tmp <- tempfile(fileext = ".RData")
download.file("https://osf.io/download/87kqz", tmp, mode = "wb")
load(tmp)
rm(list = setdiff(ls(), c("df_team", "df_tead")))
```

## Items both tools

```{r}
items_tead5 <- c(
  "tead_8", "tead_35", "tead_36", "tead_38", "tead_33",      # soc_com
  "tead_9", "tead_3", "tead_5", "tead_28", "tead_29",        # soc_inter
  "tead_70", "tead_69", "tead_4", "tead_73", "tead_66",      # sensorial
  "tead_52", "tead_59", "tead_60", "tead_63", "tead_56"      # rep_beh
)
```

```{r}
items_team4 <- c(
  "team_6", "team_11", "team_1", "team_9",      # cam
  "team_5", "team_3", "team_4", "team_25",      # gender
  "team_14", "team_22", "team_7", "team_21",    # cam2
  "team_36", "team_37", "team_32", "team_35"    # sensory
)
```

## Data TEAD

```{r}
set.seed(123)
n_total <- 700

# Eligible males and others
males <- df_tead %>%
  mutate(rowid = row_number()) %>%
  filter(complete.cases(across(all_of(items_tead5))), genero == "Masculino", aq_total <= 8)

others <- df_tead %>%
  mutate(rowid = row_number()) %>%
  filter(complete.cases(across(all_of(items_tead5))), genero != "Masculino", aq_total <= 8)

n_male <- min(n_total %/% 2, nrow(males))
n_other <- n_total - n_male

#idx_tead is a vector of row indices (rowid) for the selected participants (your analytic sample)
idx_tead  <- bind_rows(
  males %>% slice_sample(n = n_male),
  others %>% slice_sample(n = n_other)
) %>%
  sample_frac(1) %>%
  pull(rowid)
```

## Data TEAM

```{r}
set.seed(123)
idx_team <- df_team %>%
  mutate(rowid = row_number()) %>%
  filter(complete.cases(across(all_of(items_team4))), aq_total <= 6) %>%
  slice_sample(n = 700) %>%
  pull(rowid) 
```

## Compute clinical group TEAD

```{r}
df_tead <- df_tead %>%
  mutate(
    asd = grepl(
      "sim|concordo fortemente|diagnosticad[oa]|recebi|avalia[cç][aã]o neuropsicol[oó]gica.*autismo|1997.*asperger|psiquiatra.*espectro",
      voce_tem_diagnostico_de_transtorno_do_espectro_autista_tea,
      ignore.case = TRUE
    ),
    
    adhd = grepl(
      "sim|concordo fortemente",
      voce_tem_diagnostico_de_transtorno_de_deficit_de_atencao_e_hiperatividade_tdah,
      ignore.case = TRUE
    ),
    
    ocd = grepl(
      "sim|concordo|concordo fortemente|neurologista me perguntou se eu sabia que eu tenho|recebi antes de receber o diagnostico de autismo|recebi, mas nao concordo com ele",
      ja_recebi_diagnostico_de_transtorno_obsessivo_compulsivo_toc,
      ignore.case = TRUE
    )
  ) %>%
  mutate(
    clinical_group = case_when(
      asd  & !adhd & !ocd              ~ "asd",
      asd  & adhd & !ocd              ~ "asd_adhd",
      asd & ocd & !adhd               ~ "asd_ocd",
      
      adhd & !asd & !ocd               ~ "adhd",
      adhd & ocd & !asd               ~ "adhd_ocd",
      
      ocd  & !asd & !adhd              ~ "ocd",
      ocd  & adhd & asd              ~ "all_conditions",
      
      !asd & !adhd & !ocd              ~ "control",
      
      TRUE                             ~ NA_character_
    )
  )
```

## Demographic characteristics TEAD 

## Table 1

```{r}
df_tead[idx_tead, ] %>% 
  select(genero, clinical_group, idade) %>% 
  arsenal::tableby(clinical_group ~ ., data = .) %>% 
  summary(text = T, digits = 2) %>% 
  as.data.frame()
```

## ANOVA & Post Hoc tests TEAD group (itens x conditions)

```{r}
df_tead[idx_tead, ] %>%
  filter(!is.na(clinical_group)) %>%
  select(clinical_group, all_of(items_tead5)) %>%
  pivot_longer(
    cols = all_of(items_tead5),
    names_to = "item",
    values_to = "score"
  ) %>%
  filter(!is.na(score)) %>%
  group_by(item) %>%
  summarise(
    p_value = summary(aov(score ~ clinical_group))[[1]]$`Pr(>F)`[1],
    .groups = "drop"
  ) %>%
  filter(p_value < 0.05) %>%
  pull(item) %>%
  map_dfr(function(it) {
    dat <- df_tead[idx_tead, ] %>%
      filter(!is.na(clinical_group)) %>%
      select(clinical_group, score = all_of(it)) %>%
      filter(!is.na(score))
    TukeyHSD(aov(score ~ clinical_group, data = dat))$clinical_group %>%
      as.data.frame() %>%
      tibble::rownames_to_column("comparison") %>%
      mutate(item = it) %>%
      filter(`p adj` < 0.05)
  }) %>%
  ungroup() %>%
  mutate(across(where(is.numeric), ~ round(.x, 3))) %>%
  arrange(item, comparison) %>%
  select(item, comparison, diff, lwr, upr, `p adj`)
```

## Linear Regression TEAD group (age X condition)

```{r}
df_tead[idx_tead, ] %>%
  filter(
    !is.na(clinical_group),
    !is.na(idade)
  ) %>%
  mutate(
    clinical_group = relevel(factor(clinical_group), ref = "control"),
    idade_num = readr::parse_number(as.character(idade))
  ) %>%
  filter(!is.na(idade)) %>%
  lm(idade_num ~ clinical_group, data = .) %>%
  broom::tidy() %>%
  mutate(across(where(is.numeric), ~ round(.x, 3)))
```

## Overview of symptoms group comparison TEAD

```{r}
df_tead[idx_tead, ] %>%
  filter(!is.na(clinical_group)) %>%
  mutate(
    social_communication = rowSums(select(., tead_8, tead_35, tead_36, tead_38, tead_33), na.rm = TRUE),
    social_interaction = rowSums(select(., tead_9, tead_3, tead_5, tead_28, tead_29), na.rm = TRUE),
    sensorial = rowSums(select(., tead_70, tead_69, tead_4, tead_73, tead_66), na.rm = TRUE),
    repetitive_behavior = rowSums(select(., tead_52, tead_59, tead_60, tead_63, tead_56), na.rm = TRUE)
  ) %>%
  pivot_longer(
    cols = c(
      social_communication,
      social_interaction,
      sensorial,
      repetitive_behavior
    ),
    names_to = "social_emotional_skills",
    values_to = "score"
  ) %>%
  group_by(social_emotional_skills) %>%
  group_modify(~ {
    
    descriptives <- .x %>%
      group_by(clinical_group) %>%
      summarise(
        result = paste0(
          round(mean(score, na.rm = TRUE), 2),
          " (",
          round(sd(score, na.rm = TRUE), 2),
          ")"
        ),
        .groups = "drop"
      ) %>%
      pivot_wider(
        names_from = clinical_group,
        values_from = result
      )
    
    p_values <- pairwise.t.test(
      x = .x$score,
      g = .x$clinical_group,
      p.adjust.method = "bonferroni"
    )$p.value %>%
      as.table() %>%
      as.data.frame() %>%
      filter(!is.na(Freq)) %>%
      mutate(
        comparison = paste0(Var1, " x ", Var2),
        p_value = ifelse(
          Freq < .001,
          "< .001",
          as.character(round(Freq, 3))
        )
      ) %>%
      select(comparison, p_value) %>%
      pivot_wider(
        names_from = comparison,
        values_from = p_value
      )
    
    bind_cols(descriptives, p_values)
    
  }) %>%
  ungroup() 
```

# Relative Risk Autism + ADHD and Autism + OCD TEAD

```{r}
purrr::map_dfr(
  c("adhd", "ocd"),
  \(cond) {

    tab <- table(
      ASD = df_tead[idx_tead, ]$asd,
      Condition = df_tead[idx_tead, ][[cond]]
    )

    a <- tab["TRUE","TRUE"]
    b <- tab["TRUE","FALSE"]
    c <- tab["FALSE","TRUE"]
    d <- tab["FALSE","FALSE"]

    rr <- (a/(a+b)) / (c/(c+d))

    se <- sqrt((1/a) - (1/(a+b)) + (1/c) - (1/(c+d)))

    tibble::tibble(
      condition = toupper(cond),

      risk_asd = a/(a+b),
      risk_non_asd = c/(c+d),

      relative_risk = rr,

      rr_ci_low = exp(log(rr) - 1.96*se),
      rr_ci_high = exp(log(rr) + 1.96*se),

      p_value = chisq.test(tab)$p.value
    )

  }
) %>%
  mutate(across(where(is.numeric), round, 3))
```

# Commorbities Autism TEAD

```{r}
df_tead[idx_tead, ] %>%
  filter(asd) %>%
  summarise(

    n_autistas = n(),

    ADHD = sum(adhd),
    OCD = sum(ocd),

    prop_ADHD = ADHD/n_autistas,
    prop_OCD = OCD/n_autistas

  ) %>%
  mutate(

    comorbidade_mais_frequente =
      if_else(prop_ADHD > prop_OCD,
              "ADHD",
              "OCD"),

    p_value =
      df_tead[idx_tead, ] %>%
      filter(asd) %>%
      with(table(ADHD = adhd,
                 OCD = ocd)) %>%
      mcnemar.test() %>%
      .$p.value

  )
```

# Odds Ratio ADHD & OCD TEAD

```{r}
purrr::map_dfr(
  c("adhd", "ocd"),
  \(cond){

    tab <- table(
      ASD = df_tead[idx_tead, ]$asd,
      Condition = df_tead[idx_tead, ][[cond]]
    )

    a <- tab["TRUE","TRUE"]
    b <- tab["TRUE","FALSE"]
    c <- tab["FALSE","TRUE"]
    d <- tab["FALSE","FALSE"]

    or <- (a*d)/(b*c)

    se <- sqrt(1/a + 1/b + 1/c + 1/d)

    tibble::tibble(

      condition = toupper(cond),

      odds_ratio = or,

      or_ci_low = exp(log(or) - 1.96*se),

      or_ci_high = exp(log(or) + 1.96*se),

      p_value = chisq.test(tab)$p.value

    )

  }
) %>%
  mutate(across(where(is.numeric), round, 3))
```

## EFA TEAD

```{r}
efa_tead <- df_tead[idx_tead, items_tead5] 

dim(efa_tead)
sum(is.na(efa_tead))

poly_tead <- psych::polychoric(efa_tead)
R_tead <- poly_tead$rho

bartlett_tead <- psych::cortest.bartlett(
  R_tead,
  n = nrow(efa_tead)
)

bartlett_tead

kmo_tead <- psych::KMO(R_tead)

kmo_tead
kmo_tead$MSA
sort(kmo_tead$MSAi)

set.seed(123)

psych::fa.parallel(
  R_tead,
  n.obs = nrow(efa_tead),
  fa = "fa",
  fm = "minres"
)
```

# Dimensional Comparison TEAD X AQ-10

```{r}
fit_esem_aq_tead <- df_tead[idx_tead, ] %>%
  select(
    aq_1:aq_10,
    all_of(items_tead5)
  ) %>%
  mutate(across(everything(), as.numeric)) %>%
  lavaan::sem(
    model = '
      efa("efa1")*F1 +
      efa("efa1")*F2 +
      efa("efa1")*F3 +
      efa("efa1")*F4 =~
        aq_1 + aq_2 + aq_3 + aq_4 + aq_5 +
        aq_6 + aq_7 + aq_8 + aq_9 + aq_10 +
        tead_8 + tead_35 + tead_36 + tead_38 + tead_33 +
        tead_9 + tead_3 + tead_5 + tead_28 + tead_29 +
        tead_70 + tead_69 + tead_4 + tead_73 + tead_66 +
        tead_52 + tead_59 + tead_60 + tead_63 + tead_56
    ',
    estimator = "WLSMV",
    ordered = c(
      paste0("aq_", 1:10),
      items_tead5
    ),
    rotation = "geomin"
  )

fit_esem_aq_tead %>%
  lavaan::fitMeasures(
    c(
      "cfi",
      "rmsea",
      "cfi.robust",
      "rmsea.robust"
    )
  )

fit_esem_aq_tead %>%
  lavaan::standardizedSolution() %>%
  filter(op == "=~") %>%
  select(
    factor = lhs,
    item = rhs,
    loading = est.std
  ) %>%
  arrange(factor, desc(abs(loading)))
```

## Compute clinical group TEAM

```{r}
df_team <- df_team %>% 
  mutate(
    asd = grepl(
      "sim|a medica|altas|estou.*autismo|nao confiei|so em 1997",
      voce_tem_diagnostico_de_transtorno_do_espectro_autista_tea,
      ignore.case = TRUE
    ),
    
    adhd = grepl(
      "sim|concordo|5|h[aá] 2 anos",
      ja_recebi_diagnostico_de_transtorno_de_deficit_de_atencao_e_hiperatividade_tdah,
      ignore.case = TRUE
    ),
    
    ocd = grepl(
      "sim|concordo|5|j[aá] recebi mas n[aã]o acredito",
      ja_recebi_diagnostico_de_transtorno_obsessivo_compulsivo_toc,
      ignore.case = TRUE
    ),
    
    exclude = grepl(
      "sim e nao\\. na infancia fui \"diagnosticada\" mas atualmente nao sei",
      ja_recebi_diagnostico_de_transtorno_de_deficit_de_atencao_e_hiperatividade_tdah,
      ignore.case = TRUE
    ) |
      grepl(
        "sim, mas a maioria das caracteristicas foi confundida pelos profissionais, eram esteriotipias",
        ja_recebi_diagnostico_de_transtorno_obsessivo_compulsivo_toc,
        ignore.case = TRUE
      )
  ) %>% 
  mutate(
    clinical_group = case_when(
      exclude ~ NA_character_,
      
      asd & !adhd & !ocd ~ "asd",
      asd & adhd & !ocd ~ "asd_adhd",
      asd & ocd & !adhd ~ "asd_ocd",
      asd & adhd & ocd ~ "all_conditions",
      
      adhd & !asd & !ocd ~ "adhd",
      adhd & ocd & !asd ~ "adhd_ocd",
      
      ocd & !asd & !adhd ~ "ocd",
      
      !asd & !adhd & !ocd ~ "control",
      
      TRUE ~ NA_character_
    )
  )
```

## ANOVA & Post Hoc tests TEAM group (itens x conditions)

```{r}
df_team[idx_team, ] %>%
  filter(!is.na(clinical_group)) %>%
  select(clinical_group, all_of(items_team4)) %>%
  pivot_longer(
    cols = all_of(items_team4),
    names_to = "item",
    values_to = "score"
  ) %>%
  filter(!is.na(score)) %>%
  group_by(item) %>%
  summarise(
    p_value = summary(aov(score ~ clinical_group))[[1]]$`Pr(>F)`[1],
    .groups = "drop"
  ) %>%
  filter(p_value < 0.05) %>%
  pull(item) %>%
  map_dfr(function(it) {
    dat <- df_team[idx_team, ] %>%
      filter(!is.na(clinical_group)) %>%
      select(clinical_group, score = all_of(it)) %>%
      filter(!is.na(score))
    TukeyHSD(aov(score ~ clinical_group, data = dat))$clinical_group %>%
      as.data.frame() %>%
      tibble::rownames_to_column("comparison") %>%
      mutate(item = it) %>%
      filter(`p adj` < 0.05)
  }) %>%
  ungroup() %>%
  mutate(across(where(is.numeric), ~ round(.x, 3))) %>%
  arrange(item, comparison) %>%
  select(item, comparison, diff, lwr, upr, `p adj`)
```

## Demographic characteristics TEAM 

## Table 1

```{r}
df_team[idx_team, ] %>% 
  select(genero, clinical_group, idade) %>% 
  arsenal::tableby(clinical_group ~ ., data = .) %>% 
  summary(text = T, digits = 2) %>% 
  as.data.frame()
```
## Linear Regression TEAM group (age X condition)

```{r}
df_team[idx_team, ] %>%
  filter(
    !is.na(clinical_group),
    !is.na(qual_e_a_sua_idade_em_numeros)
  ) %>%
  mutate(
    clinical_group = relevel(factor(clinical_group), ref = "control"),
    idade_num = readr::parse_number(as.character(qual_e_a_sua_idade_em_numeros))
  ) %>%
  filter(!is.na(idade_num)) %>%
  lm(idade_num ~ clinical_group, data = .) %>%
  broom::tidy() %>%
  mutate(across(where(is.numeric), ~ round(.x, 3)))
```

## ANOVA & Post Hoc tests TEAM group (itens x conditions + age)

```{r}
df_team[idx_team, ] %>%
  filter(
    !is.na(clinical_group),
    !is.na(qual_e_a_sua_idade_em_numeros)
  ) %>%
  mutate(
    idade_num = readr::parse_number(as.character(qual_e_a_sua_idade_em_numeros)),
    clinical_group = as.factor(clinical_group)
  ) %>%
  select(clinical_group, idade_num, all_of(items_team4)) %>%
  pivot_longer(
    cols = all_of(items_team4),
    names_to = "item",
    values_to = "score"
  ) %>%
  filter(
    !is.na(score),
    !is.na(idade_num)
  ) %>%
  group_by(item) %>%
  group_modify(~ {
    
    modelo <- lm(score ~ clinical_group + idade_num, data = .x)
    
    anova_model <- anova(modelo)
    
    p_group <- anova_model["clinical_group", "Pr(>F)"]
    
    if (!is.na(p_group) && p_group < 0.05) {
      
      pairwise.t.test(
        x = .x$score,
        g = .x$clinical_group,
        p.adjust.method = "bonferroni"
      ) %>%
        broom::tidy() %>%
        filter(p.value < 0.05)
      
    } else {
      tibble()
    }
    
  }) %>%
  ungroup() %>%
  mutate(across(where(is.numeric), ~ round(.x, 3))) %>%
  arrange(item)
```

## Descriptive statistics and overview of group comparison TEAM

```{r}
df_team[idx_team, ] %>%
  filter(!is.na(clinical_group)) %>%
  mutate(
    camouflage_ca = rowSums(select(., team_6, team_11, team_1, team_9), na.rm = TRUE),
    gender_self_id = rowSums(select(., team_5, team_3, team_4, team_25), na.rm = TRUE),
    camouflage_m = rowSums(select(., team_14, team_22, team_7, team_21), na.rm = TRUE),
    sensory_sensitivity = rowSums(select(., team_36, team_37, team_32, team_35), na.rm = TRUE)
  ) %>%
  pivot_longer(
    cols = c(
      camouflage_ca,
      gender_self_id,
      camouflage_m,
      sensory_sensitivity
    ),
    names_to = "social_emotional_skills",
    values_to = "score"
  ) %>%
  group_by(social_emotional_skills) %>%
  group_modify(~ {
    
    descriptives <- .x %>%
      group_by(clinical_group) %>%
      summarise(
        result = paste0(
          round(mean(score, na.rm = TRUE), 2),
          " (",
          round(sd(score, na.rm = TRUE), 2),
          ")"
        ),
        .groups = "drop"
      ) %>%
      pivot_wider(
        names_from = clinical_group,
        values_from = result
      )
    
    p_values <- pairwise.t.test(
      x = .x$score,
      g = .x$clinical_group,
      p.adjust.method = "bonferroni"
    )$p.value %>%
      as.table() %>%
      as.data.frame() %>%
      filter(!is.na(Freq)) %>%
      mutate(
        comparison = paste0(Var1, " x ", Var2),
        p_value = ifelse(
          Freq < .001,
          "< .001",
          as.character(round(Freq, 3))
        )
      ) %>%
      select(comparison, p_value) %>%
      pivot_wider(
        names_from = comparison,
        values_from = p_value
      )
    
    bind_cols(descriptives, p_values)
    
  }) %>%
  ungroup() %>%
  select(
    social_emotional_skills,
    adhd,
    asd,
    control,
    ocd,
    everything()
  ) %>%
  arrange(social_emotional_skills)
```

# Relative Risk Autism + ADHD and Autism + OCD TEAM

```{r}
purrr::map_dfr(
  c("adhd", "ocd"),
  \(cond) {

    tab <- table(
      ASD = df_team[idx_team, ]$asd,
      Condition = df_team[idx_team, ][[cond]]
    )

    a <- tab["TRUE","TRUE"]
    b <- tab["TRUE","FALSE"]
    c <- tab["FALSE","TRUE"]
    d <- tab["FALSE","FALSE"]

    rr <- (a/(a+b)) / (c/(c+d))

    se <- sqrt((1/a) - (1/(a+b)) + (1/c) - (1/(c+d)))

    tibble::tibble(
      condition = toupper(cond),

      risk_asd = a/(a+b),
      risk_non_asd = c/(c+d),

      relative_risk = rr,

      rr_ci_low = exp(log(rr) - 1.96*se),
      rr_ci_high = exp(log(rr) + 1.96*se),

      p_value = chisq.test(tab)$p.value
    )

  }
) %>%
  mutate(across(where(is.numeric), round, 3))
```

# Commorbities Autism TEAD

```{r}
df_team[idx_team, ] %>%
  filter(asd) %>%
  summarise(

    n_autistas = n(),

    ADHD = sum(adhd),
    OCD = sum(ocd),

    prop_ADHD = ADHD/n_autistas,
    prop_OCD = OCD/n_autistas

  ) %>%
  mutate(

    comorbidade_mais_frequente =
      if_else(prop_ADHD > prop_OCD,
              "ADHD",
              "OCD"),

    p_value =
      df_team[idx_team, ] %>%
      filter(asd) %>%
      with(table(ADHD = adhd,
                 OCD = ocd)) %>%
      mcnemar.test() %>%
      .$p.value

  )
```

# Odds Ratio ADHD & OCD TEAD

```{r}
purrr::map_dfr(
  c("adhd", "ocd"),
  \(cond){

    tab <- table(
      ASD = df_team[idx_team, ]$asd,
      Condition = df_team[idx_team, ][[cond]]
    )

    a <- tab["TRUE","TRUE"]
    b <- tab["TRUE","FALSE"]
    c <- tab["FALSE","TRUE"]
    d <- tab["FALSE","FALSE"]

    or <- (a*d)/(b*c)

    se <- sqrt(1/a + 1/b + 1/c + 1/d)

    tibble::tibble(

      condition = toupper(cond),

      odds_ratio = or,

      or_ci_low = exp(log(or) - 1.96*se),

      or_ci_high = exp(log(or) + 1.96*se),

      p_value = chisq.test(tab)$p.value

    )

  }
) %>%
  mutate(across(where(is.numeric), round, 3))
```

## EFA TEAM

```{r}
efa_team <- df_team[idx_team, items_team4]

dim(efa_team)
sum(is.na(efa_team))

poly_team <- psych::polychoric(efa_team)
R_team <- poly_team$rho

bartlett_team <- psych::cortest.bartlett(
  R_team,
  n = nrow(efa_team)
)

bartlett_team

kmo_team <- psych::KMO(R_team)

kmo_team
kmo_team$MSA
sort(kmo_team$MSAi)

set.seed(123)

psych::fa.parallel(
  R_team,
  n.obs = nrow(efa_team),
  fa = "fa",
  fm = "minres"
)
```

# Dimensional Comparison TEAM X AQ-10

```{r}
fit_esem_aq_team <- df_team[idx_team, ] %>%
  select(
    aq_1:aq_10,
    all_of(items_team4)
  ) %>%
  mutate(across(everything(), as.numeric)) %>%
  lavaan::sem(
    model = '
      efa("efa1")*F1 +
      efa("efa1")*F2 +
      efa("efa1")*F3 +
      efa("efa1")*F4 =~
        aq_1 + aq_2 + aq_3 + aq_4 + aq_5 +
        aq_6 + aq_7 + aq_8 + aq_9 + aq_10 +
        team_6 + team_11 + team_1 + team_9 +
        team_5 + team_3 + team_4 + team_25 +
        team_14 + team_22 + team_7 + team_21 +
        team_36 + team_37 + team_32 + team_35
    ',
    estimator = "WLSMV",
    ordered = c(
      paste0("aq_", 1:10),
      items_team4
    ),
    rotation = "geomin"
  )

fit_esem_aq_team %>%
  lavaan::fitMeasures(
    c(
      "cfi",
      "rmsea",
      "cfi.robust",
      "rmsea.robust"
    )
  )

fit_esem_aq_team %>%
  lavaan::standardizedSolution() %>%
  filter(op == "=~") %>%
  select(
    factor = lhs,
    item = rhs,
    loading = est.std
  ) %>%
  arrange(factor, desc(abs(loading)))
```
